manuscript

### 2023-12-01 scripts/manuscript.qmd
One code suggestion

```{r}
#| echo: FALSE
communication <- import(here("data", "communication.csv"))
communication <- (clean_names(communication))
```

>>>>

```{r}
#| echo: FALSE
communication <- import(here("data", "communication.csv")) %>% 
  clean_names()
```

Instead of feeding the data into the the `clean_name()` function with another line of code, I suggest piping it directly into `clean_name()`. I borrowed this from Dr.Nese's slides and found it convenient.
